---
title: "Discrete Math Exercises"
author: "Quizlet"
date: "`r Sys.Date()`"
output: 
  rmdformats::downcute:
    toc_depth: 3
    highlight: pygments
---

```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = FALSE)
knitr::opts_chunk$set(echo = TRUE)
```
###### Discrete Mathematics and Its Applications (8th Edition)
<br>

```{r mathLink, include=FALSE}
# Mathematical Notations/Symbols for R-markdown
# https://rpruim.github.io/s341/S19/from-class/MathinRmd.html
```


```{r libraries, include=FALSE}
library(rmdformats)
library(vembedr)
library(reticulate)
```
<hr>

## Chapter 1The Foundations: Logic and Proofs
<hr>

### Exercise 1a {.tabset .tabset-fade}

#### Step-1

In this exercise, we determine whether the given statement represents a proposition.

**What is a proposition?**

<br>

#### Step-2

A **proposition** is a statement that is known to be true or known to be false. If we don't know if a statement is true or false, then the statement is not a proposition.

<br>

#### Step-3

**(a)**

The statement is a proposition because we know that the statement is true 
$T$ *(as Boston is the capital of Massachusetts)*.

<br>

#### Step-4

Let us summarize how the results were derived.

To determine whether a statement is a proposition, we determined whether the statement was true or false.

If we were able to derive a truth value, then the statement has to be a proposition.
If we were unable to assign a truth value to the statement or the truth value was dependent on some variable, then the statement couldn't be a proposition.

<br>

#### Results

*(a) Proposition, $T$*

<br><br />

<br><br />


### Exercise 1b {.tabset .tabset-fade}

#### Step-1

In this exercise, we determine whether the given statement represents a proposition.

**What is a proposition?**

<br>

#### Step-2

A **proposition** is a statement that is known to be true or known to be false. If we don't know if a statement is true or false, then the statement is not a proposition.

<br>

#### Step-3

(b)

The statement is a proposition because we know that the statement is false $F$ *(as Tallahassee is the capital of Florida)*.

<br>

#### Step-4

Let us summarize how the results were derived.

To determine whether a statement is a proposition, we determined whether the statement was true or false.

  - If we were able to derive a truth value, then the statement has to be a proposition.
  - If we were unable to assign a truth value to the statement or the truth value was dependent on some variable, then the statement couldn't be a proposition.

<br>

#### Results

*(b) Proposition, $F$*

<br><br />

<br><br />


### Exercise 1c {.tabset .tabset-fade}

#### Step-1

In this exercise, we determine whether the given statement represents a proposition.

**What is a proposition?**

<br>

#### Step-2

A **proposition** is a statement that is known to be true or known to be false. If we don't know if a statement is true or false, then the statement is not a proposition.

<br>

#### Step-3

**(c)**

The statement is a proposition because we know that the statement is true 
$T$ *(since 2 added to 3 is equal to 5)*.

<br>

#### Step-4

Let us summarize how the results were derived.

To determine whether a statement is a proposition, we determined whether the statement was true or false.

  - If we were able to derive a truth value, then the statement has to be a proposition.
  - If we were unable to assign a truth value to the statement or the truth value was dependent on some variable, then the statement couldn't be a proposition.

<br>

#### Results

*(c) Proposition, $T$*

<br><br />

<br><br />


### Exercise 1d {.tabset .tabset-fade}

#### Step-1

In this exercise, we determine whether the given statement represents a proposition.

**What is a proposition?**

<br>

#### Step-2

A **proposition** is a statement that is known to be true or known to be false. If we don't know if a statement is true or false, then the statement is not a proposition.

<br>

#### Step-3

**(d)**

The statement is a proposition because we know that the statement is false $F$ 
*(since 5 added to 7 is equal to 12, and thus not equal to 10)*.

<br>

#### Step-4

Let us summarize how the results were derived.

To determine whether a statement is a proposition, we determined whether the statement was true or false.

  - If we were able to derive a truth value, then the statement has to be a proposition.
  - If we were unable to assign a truth value to the statement or the truth value was dependent on some variable, then the statement couldn't be a proposition.

<br>

#### Results

*(d) Proposition, $F$*

<br><br />

<br><br />



### Exercise 1e {.tabset .tabset-fade}

#### Step-1

In this exercise, we determine whether the given statement represents a proposition.

**What is a proposition?**

<br>

#### Step-2

A **proposition** is a statement that is known to be true or known to be false. If we don't know if a statement is true or false, then the statement is not a proposition.

<br>

#### Step-3

**(e)**

The statement is not a proposition, because the statement could be true or could be **false** *(but we do not know which case since $x$ is unknown)*.

<br>

#### Step-4

Let us summarize how the results were derived.

To determine whether a statement is a proposition, we determined whether the statement was true or false.

  - If we were able to derive a truth value, then the statement has to be a proposition.
  - If we were unable to assign a truth value to the statement or the truth value was dependent on some variable, then the statement couldn't be a proposition.

<br>

#### Results

*(e) Not a proposition*

<br><br />

<br><br />



### Exercise 1f {.tabset .tabset-fade}

#### Step-1

In this exercise, we determine whether the given statement represents a proposition.

**What is a proposition?**

<br>

#### Step-2

A **proposition** is a statement that is known to be true or known to be false. If we don't know if a statement is true or false, then the statement is not a proposition.

<br>

#### Step-3

**(f)**

The statement is not a proposition, because it is not a statement that could be true or false.

<br>

#### Step-4

Let us summarize how the results were derived.

To determine whether a statement is a proposition, we determined whether the statement was true or false.

  - If we were able to derive a truth value, then the statement has to be a proposition.
  - If we were unable to assign a truth value to the statement or the truth value was dependent on some variable, then the statement couldn't be a proposition.

<br>

#### Results

*(f) Not a proposition*

<br><br />

<br><br />



### Exercise 2a {.tabset .tabset-fade}

#### Step-1

**PART A:** This sentence is not a proposition because it is not a declarative sentence. 

So it is not possible for this sentence to be true or false.

<br>

#### Step-2

PART A: not a proposition

<br><br />

<br><br />



### Exercise 2b {.tabset .tabset-fade}

#### Step-1

*PART B:* This sentence is not a proposition because it is not a declarative sentence. 

So it is not possible for this sentence to be true or false.

<br>

#### Step-2

*PART B: not a proposition*

<br><br />

<br><br />




### Exercise 2c {.tabset .tabset-fade}

#### Step-1

**PART C:** This sentence is a proposition because it can either be true or false. 

Its truth value is false because black flies exist everywhere.

<br>

#### Step-2

*PART C: proposition, false*

<br><br />

<br><br />




### Exercise 2d {.tabset .tabset-fade}

#### Step-1

**PART D:** This sentence is not a proposition because the value of $x$ is not given. 

So it is not possible for this sentence to be true or false.

<br>

#### Step-2

*PART D: not a proposition*

<br><br />

<br><br />



### Exercise 2e {.tabset .tabset-fade}

#### Step-1

**PART E:** This sentence is a proposition because it can either be true or false. 

Its truth value is false because the moon is not made from green cheese.

<br>

#### Step-2

*PART E: proposition, false*

<br><br />

<br><br />



### Exercise 2f {.tabset .tabset-fade}

#### Step-1

PART F: This sentence is not a proposition because the value of $n$ is not given. 

So it is not possible for this sentence to be true or false.

<br>

#### Step-2

*PART F: not a proposition*

<br><br />

<br><br />



### Exercise 3 {.tabset .tabset-fade}

#### Step-1

**(a)**

<center>$\text{ Linda is younger than Sanjay. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Linda is not younger than Sanjay. }$</center>

*Note: This sentence is also equivalent with: Linda is older or the same age as Sanjay.*

<br>

#### Step-2

**(b)**

<center>$\text{ Mei makes more money than Isabella. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Mei does not make more money than Isabella. }$</center>

*Note: This sentence is also equivalent with: Mei makes less money or the same amount of money than Isabella.*

<br>

#### Step-3

**(c)**

<center>$\text{ Moshe is taller than Monica. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Moshe is not taller than Monica. }$</center>

*Note: This sentence is also equivalent with: Moshe is shorter or the same height as Monica.*

<br>

#### Step-4

**(d)**

<center>$\text{ Abby is richer than Ricardo. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Abby is not richer than Ricardo. }$</center>

*Note: This sentence is also equivalent with: Abby is poorer or equally rich to Ricardo.*

<br>

#### Results
<br>


<center>**(a)** Linda is not younger than Sanjay.</center>

<center>**(b)** Mei does not make more money than Isabella.</center>

<center>**(c)** Moshe is not taller than Monica.</center>

<center>**(d)** Abby is not richer than Ricardo.</center>


<br><br />

<br><br />



### Exercise 4 {.tabset .tabset-fade}

#### Step-1

**(a)**

<center>$\text{ Janice has more Facebook friends than Juan. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Janice does not have more Facebook friends than Juan. }$</center>

*Note: This sentence is also equivalent with: Janice has less Facebook friends or the same number of Facebook friends as Juan.*

<br>

#### Step-2

**(b)** 

<center>$\text{ Quincy is smarter than Venkat. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Quincy is not smarter than Venkat. }$</center>

*Note: This sentence is also equivalent with: Quincy is dumber or equally intelligent as Venkat.*

<br>

#### Step-3

**(c)**

<center>$\text{ Zelda drives more miles to school than Paola. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Zelda does not drive more miles to school than Paola. }$</center>

*Note: This sentence is also equivalent with: Zelda drives less miles or the same number of miles to school than Paola.*

<br>

#### Step-4

**(d)**

<center>$\text{ Brianna sleeps longer than Gloria. }$</center>

The negation of the proposition adds the word "not" to the sentence:

<center>$\text{ Brianna does not sleep longer than Gloria. }$</center>

*Note: This sentence is also equivalent with: Brianna sleeps less or the same amount than Gloria.*

<br>

#### Results
<br>

<center>**(a)** Janice does not have more Facebook friends than Juan.</center>

<center>**(b)** Quincy is not smarter than Venkat.</center>

<center>**(c)** Zelda does not drive more miles to school than Paola.</center>

<center>**(d)** Brianna does not sleep longer than Gloria.</center>


<br><br />

<br><br />



### Exercise 5a {.tabset .tabset-fade}

#### Step-1

**DEFINITIONS**

The negation of a statement states the opposite of the given statement.

<br>

#### Step-2

**SOLUTION**

**(a)** The opposite of a statement can be obtained by adding "not" to the given statement. The opposite of Mei having an MP3 player is that Mei does not have an MP3 player.

<br>

#### Step-3
<br>

*(a) Mei does not have an MP3 player.*


<br><br />

<br><br />




### Exercise 5b {.tabset .tabset-fade}

#### Step-1

**DEFINITIONS**

The negation of a statement states the opposite of the given statement.

<br>

#### Step-2

**SOLUTION**

**(b)** The opposite of no pollution in New Jersey is that there is pollution in New Jersey.

<br>

#### Step-3
<br>

*(b) There is pollution in New Jersey.*


<br><br />

<br><br />



### Exercise 5c {.tabset .tabset-fade}

#### Step-1

**DEFINITIONS**

The negation of a statement states the opposite of the given statement.

<br>

#### Step-2

**SOLUTION**

**(c)** The opposite of an equality $(=)$ is a difference $\text{(≠)   2+1 ≠ 3 }$

<br>

#### Step-3
<br>

*(c) $2+1 ≠ 3$*


<br><br />

<br><br />



### Exercise 5d {.tabset .tabset-fade}

#### Step-1

**DEFINITIONS**

The negation of a statement states the opposite of the given statement.

<br>

#### Step-2

**SOLUTION**

**(d)** The opposite of a statement can be obtained by adding *"not"* to the given statement: The summer in Maine is not *(hot and sunny)*.

<br>

#### Step-3

*(d) The summer in Maine is not (hot and sunny).*


<br><br />

<br><br />




<!-- ### Exercise  {.tabset .tabset-fade} -->

<!-- #### Step-1 -->

<!-- - -->

<!-- <br> -->

<!-- #### Step-2 -->

<!-- - -->

<!-- <br> -->

<!-- #### Step-3 -->

<!-- **(d)** -->

<!-- - -->

<!-- <br> -->

<!-- #### Step-4 -->

<!-- - -->

<!-- <br> -->

<!-- #### Results -->

<!-- - -->

<!-- <br><br /> -->

<!-- <br><br /> -->


### Exercise 7a {.tabset .tabset-fade}

#### Step-1

**DEFINITION**

The negation of a statement states the opposite of the given statement.

<br>

#### Step-2

**(a)** The opposite of a statement can be obtained by adding "not" to the given statement 

*(note: adjust the sentence such that it remains proper English):*
  - Steve does not have more than 100 GB free disk space on his laptop.

<br>

#### Step-3
<br>

*(a) Steve does not have more than 100 GB free disk space on his laptop.*


<br><br />

<br><br />



### Exercise 7b {.tabset .tabset-fade}

#### Step-1

**DEFINITION**

The negation of a statement states the opposite of the given statement.

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />




### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />



### Exercise  {.tabset .tabset-fade}

#### Step-1

-

<br>

#### Step-2

-

<br>

#### Step-3

**(d)**

-

<br>

#### Step-4

-

<br>

#### Results

-

<br><br />

<br><br />


